Evaluating the Effects of Tracker Reliability and Field of View on a Target Following Task in Augmented Reality

### 2009-08-25 trunk/Paper/paper.tex
changed interaction figure

@@

\keywords{
%radiosity, global illumination, constant time
}

%%%%%% START OF THE PAPER %%%%%%
%
\def\sharedaffiliation{%
\end{tabular}
\begin{tabular}{c}}
%
\begin{document}

@@

\begin{CRcatlist}
%  \CRcat{K.6.1}{Management of Computing and Information Systems}{Project and People Management}{Life Cycle};
%  \CRcat{K.7.m}{The Computing Profession}{Miscellaneous}{Ethics}
\end{CRcatlist}

@@

%% \copyrightspace

@@

We also used a two-way {ANOVA} to examine the number of times the participant loses the target, with results shown in Figure \ref{fig:anova}.  Both field of view and dropout length have a significant effect at the $p=0.001$ level.  There also is an interaction between the two factors at the $p=0.05$ level.  Figure \ref{fig:interaction} shows a plot of this interaction.  
% TODO: need F values reported here.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=2.5in]{figures/numtimes_interaction.pdf}
	\caption{\label{fig:interaction}Interaction plot of the effect of field of view and sensor dropout length on the number of times the participant loses the target.}
\end{figure}

@@

To investigate this threshold, we had seven participants complete an extra three trials with the medium field of view and sensor dropout periods of 0.5 seconds.  Figure \ref{fig:extra} shows a box plot of time following target versus sensor dropout length for these seven participants.  Again using Tukey's HSD to compare the means, we did not find a significant difference between the zero length and half second length conditions, but did find a significant difference between those and the higher length conditions.
%TODO: table with values
With further experimentation, we could further delineate the performance curve as the dropout length increases from zero to one.

\begin{figure}[htb]
	\centering
	\includegraphics[width=2.5in]{figures/extra.pdf}
	\caption{\label{fig:extra}Box plot of the total time the participant is following the target versus the length of the sensor dropout periods, including the half second dropout condition.  We collected this data from seven participants, using the medium field of view.}
\end{figure}

@@

%\section*{Acknowledgements}
%Cha Lee, Steffen Gauglitz, funding, and all of our participants.

\bibliographystyle{acmsiggraph}
\bibliography{paper}
\end{document}

>>>>

\usepackage{subfigure}

@@

\keywords{
augmented reality, immersion, user study, simulation 
}

%%%%%% START OF THE PAPER %%%%%%
\begin{document}

@@

\begin{CRcatlist}
  \CRcat{I.3.7}{Computer Graphics}{Three-Dimensional Graphics and Realism}{Augmented Reality};
  \CRcat{H.1.2}{Models and Principles}{User/Machine Systems}{Human Factors};
\end{CRcatlist}

@@

\copyrightspace

@@

We also used a two-way {ANOVA} to examine the number of times the participant loses the target, with results shown in Figure \ref{fig:anova}.  Both field of view and dropout length have a significant effect at the $p=0.001$ level.  There also is an interaction between the two factors at the $p=0.05$ level.  Figures \ref{subfig:low}-(c) show box plots for these conditions.  
% TODO: need F values reported here.

@@

%\begin{figure}[t]
%	\centering
%	\includegraphics[width=2.5in]{figures/numtimes_interaction.pdf}
%	\caption{\label{fig:interaction}Interaction plot of the effect of field of view and sensor dropout length on the number of times the participant loses the target.}
%\end{figure}

%\begin{figure*}[t]
%	\centering
%	\subfigure[]{\label{subfig:low}\includegraphics[width=1.5in]{figures/numtimes_deadlen_lowfov.pdf}}
%	\subfigure[]{\label{subfig:med}\includegraphics[width=1.5in]{figures/numtimes_deadlen_medfov.pdf}}
%	\subfigure[]{\label{subfig:upp}\includegraphics[width=1.5in]{figures/numtimes_deadlen_uppfov.pdf}}
%	\caption{\label{fig:interaction}Box plots relating sensor dropout length to the number of times the participant loses the target, with (a) low, (b) medium and (c) upper field of view.}
%\end{figure*}

%\begin{figure}[h]
%	\centering
%	\includegraphics[width=1.5in]{figures/extra.pdf}
%	\caption{\label{fig:extra}Box plot of the total time the participant is following the target versus the length of the sensor dropout periods, including the half second dropout condition.  We collected this data from seven participants, using the medium field of view.}
%\end{figure}

\begin{figure*}[t]
	\centering
	\subfigure[]{\label{subfig:low}\includegraphics[width=1.7in]{figures/numtimes_deadlen_lowfov.pdf}}
	\subfigure[]{\label{subfig:med}\includegraphics[width=1.7in]{figures/numtimes_deadlen_medfov.pdf}}
	\subfigure[]{\label{subfig:upp}\includegraphics[width=1.7in]{figures/numtimes_deadlen_uppfov.pdf}}
	\subfigure[]{\label{subfig:extra}\includegraphics[width=1.7in]{figures/extra.pdf}}
	\caption{\label{fig:interaction}Box plots (a)-(c) relate sensor dropout length to the number of times the participant loses the target, with (a) low, (b) medium and (c) upper field of view.  Box plot (d) shows the total time the participant is following the target versus the length of the sensor dropout periods, including the half second dropout condition.  We collected the data for box plot (d) from seven participants, using the medium field of view.}
\end{figure*}

@@

To investigate this threshold, we had seven participants complete an extra three trials with the medium field of view and sensor dropout periods of 0.5 seconds.  Figure \ref{subfig:extra} shows a box plot of time following target versus sensor dropout length for these seven participants.  Again using Tukey's HSD to compare the means, we did not find a significant difference between the zero length and half second length conditions, but did find a significant difference between those and the higher length conditions.
%TODO: table with values
With further experimentation, we could further delineate the performance curve as the dropout length increases from zero to one.

@@

\section*{Acknowledgements}
We would like to thank Cha Lee and Steffen Gauglitz for help in designing and running our experiments, and our study participants.  This work was partially supported by NSF CAREER grant IIS-0747520, and NSF IGERT grant DGE-0221713.

\bibliographystyle{acmsiggraph}
\bibliography{paper}

\end{document}
